Supplementary Figures---``\emph{scater:} pre-processing, quality control, normalisation and visualisation of single-cell RNA-seq data in R''

### 2016-11-06 supplement_figs_biorxiv.tex
Revisions to manuscript for resubmission

\documentclass{revtex4}
\usepackage{hyperref}
\usepackage{graphicx}
\begin{document}

\title[scater supplementary figures]{Supplementary Figures---``\emph{scater:} pre-processing, quality control, normalisation and visualisation of single-cell RNA-seq data in R''}
\author{Davis J.~McCarthy\,$^{\text{1,2,5}*}$, Kieran R.~Campbell\,$^{\text{2,4}}$, Aaron T.~L.~Lun\,$^{\text{6}}$ and Quin F.~Wills\,$^{\text{2,3}}$}
\address{$^{\text{1}}$European Molecular Biology Laboratory - European Bioinformatics Institute (EMBL-EBI), Hinxton CB10 1SD, United Kingdom;\\
$^{\text{2}}$Wellcome Trust Centre for Human Genetics, University of Oxford,
Roosevelt Drive, Oxford OX3 7BN, United Kingdom;\\
$^{\text{3}}$Weatherall Institute for Molecular Medicine, University of Oxford, John Radcliffe Hospital, Oxford OX3 9DS, United Kingdom;\\
$^{\text{4}}$Department of Physiology, Anatomy and Genetics, University of Oxford, South Parks Road, Oxford OX1 3QX, United Kingdom;\\
$^{\text{5}}$St Vincent's Institute of Medical Research, 41 Victoria Parade, Fitzroy Victoria 3065, Australia; and \\
$^{\text{6}}$CRUK Cambridge Institute, University of Cambridge, Robinson Way, Cambridge CB2 0RE, United Kingdom.
% $^{\text{\sf 4}}$Department of Statistics, University of Oxford, Oxford, Oxfordshire, UK;
}

\begin{abstract}
Supplementary material and figures---details of package dependencies; an overview of the SCESet class; an overview of the \emph{scater} ecosystem; examples of using the \emph{scater} GUI.\\ \\
\textbf{Contact:} \href{davis@ebi.ac.uk}{davis@ebi.ac.uk}
\end{abstract}

\maketitle

@@

\paragraph{Pseudotime estimation with \emph{monocle}} As with clustering, current pseudotime estimation methods do not internally account for batch effects. Thus, before applying pseudotime tools, data should be QC'd with \emph{scater} to remove problematic cells and genes. Size-factor normalisation of data is advisable, and the normaliseExprs function in \emph{scater} can be used to regress out known batch or technical effects. Once a filtered and normalised SCESet object has been obtained, the convertTo function in \emph{scran} can be used to convert the SCESet object to a CellDataSet object used in \emph{monocle}.

@@

\begin{figure}[!tpb]%figure2
\centerline{\includegraphics[width=0.95\textwidth]{figures/sceset_outline.pdf}}
\caption{An overview of the SCESet class that underpins the \emph{scater} package. Building on Bioconductor's ExpressionSet class, it is a fully-featured, sophisticated and flexible data class tailored to scRNA-seq data.}\label{fig:02}
\end{figure}

@@

\bibliographystyle{natbib}
%\bibliographystyle{achemnat}
%\bibliographystyle{plainnat}
%\bibliographystyle{abbrv}
%\bibliographystyle{plain}
%\bibliographystyle{bioinformatics}
\bibliography{main}

>>>>

\documentclass[10pt,letterpaper]{article}
\usepackage[top=0.85in,left=2.75in,footskip=0.75in,marginparwidth=2in]{geometry}

% use Unicode characters - try changing the option if you run into troubles with special characters (e.g. umlauts)
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}

% clean citations
%\usepackage{cite}
\usepackage[round]{natbib}

% hyperref makes references clicky. use \url{www.example.com} or \href{www.example.com}{description} to add a clicky url
\usepackage{nameref,hyperref}

% line numbers
\usepackage[right]{lineno}

% improves typesetting in LaTeX
\usepackage{microtype}
\DisableLigatures[f]{encoding = *, family = * }

% text layout - change as needed
\raggedright
\setlength{\parindent}{0.5cm}
\textwidth 5.25in
\textheight 8.75in

% use adjustwidth environment to exceed text width (see examples in text)
\usepackage{changepage}

% adjust caption style
%\usepackage[labelfont=bf,labelsep=period,singlelinecheck=off]{caption}

% remove brackets from references
\makeatletter
\renewcommand{\@biblabel}[1]{\quad#1.}
\makeatother

% headrule, footrule and page numbers
\usepackage{lastpage,fancyhdr,graphicx}
\usepackage{epstopdf}
\pagestyle{myheadings}
\pagestyle{fancy}
\fancyhf{}
\rfoot{\thepage/\pageref{LastPage}}
\renewcommand{\footrule}{\hrule height 2pt \vspace{2mm}}
\fancyheadoffset[L]{2.25in}
\fancyfootoffset[L]{2.25in}

% use \textcolor{color}{text} for colored text (e.g. highlight to-do areas)
\usepackage{color}

% define custom colors (this one is for figure captions)
\definecolor{Gray}{gray}{.25}

% this is required to include graphics
\usepackage{graphicx}

% use if you want to put caption to the side of the figure - see example in text
\usepackage{sidecap}

% use for have text wrap around figures
\usepackage{wrapfig}
\usepackage[pscoord]{eso-pic}
\usepackage[fulladjust]{marginnote}
\reversemarginpar

% document begins here
\begin{document}
\vspace*{0.35in}

% title goes here:
\begin{flushleft}
{\Large
\textbf\newline{Supplementary Material and Figures---\emph{scater:} pre-processing, quality control, normalisation and visualisation of single-cell RNA-seq data in R}
}
\newline
% authors go here:
\\
Davis J.~McCarthy\,\textsuperscript{1,2,5,*},
Kieran R.~Campbell\,\textsuperscript{2,4},
Aaron T.~L.~Lun\,\textsuperscript{6},
Quin F.~Wills\,\textsuperscript{2,3}
\\
\bigskip
\bf{1} European Molecular Biology Laboratory - European Bioinformatics Institute (EMBL-EBI), Hinxton CB10 1SD, United Kingdom;
\\
\bf{2} Wellcome Trust Centre for Human Genetics, University of Oxford,
Roosevelt Drive, Oxford OX3 7BN, United Kingdom;
\\
\bf{3} Weatherall Institute for Molecular Medicine, University of Oxford, John Radcliffe Hospital, Oxford OX3 9DS, United Kingdom;
\\
\bf{4} Department of Physiology, Anatomy and Genetics, University of Oxford, South Parks Road, Oxford OX1 3QX, United Kingdom;
\\
\bf{5} St Vincent's Institute of Medical Research, 41 Victoria Parade, Fitzroy Victoria 3065, Australia; and
\\
\bf{6} CRUK Cambridge Institute, University of Cambridge, Robinson Way, Cambridge CB2 0RE, United Kingdom.
\\
\bigskip
* \textbf{Contact:} \href{davis@ebi.ac.uk}{davis@ebi.ac.uk}

\end{flushleft}

\section*{Abstract}
Supplementary material and figures---details of package dependencies; entry points for common third-party tools from \emph{scater}; an overview of the SCESet class; an overview of the \emph{scater} ecosystem; examples of using the \emph{scater} GUI.\\ \noindent
\textbf{Contact:} \href{davis@ebi.ac.uk}{davis@ebi.ac.uk}

% now start line numbers
\linenumbers

@@

\paragraph{Pseudotime estimation with \emph{monocle}} As with clustering, current pseudotime estimation methods do not internally account for batch effects. Thus, before applying pseudotime tools, data should be QC'd with \emph{scater} to remove problematic cells and genes. Size-factor normalisation of data is advisable, and the normaliseExprs function in \emph{scater} can be used to regress out known batch or technical effects. Once a filtered and normalised SCESet object has been obtained, the convertTo function in \emph{scran} can be used to convert the SCESet object to a CellDataSet object used in \emph{monocle}. \newline

@@

\begin{figure}[!htpb]%figure2
\centerline{\includegraphics[width=0.95\textwidth]{figures/sceset_outline.pdf}}
\caption{An overview of the SCESet class that underpins the \emph{scater} package. Building on Bioconductor's ExpressionSet class, it is a fully-featured, sophisticated and flexible data class tailored to scRNA-seq data.}\label{fig:02}
\end{figure}

@@

\clearpage

\nolinenumbers

\bibliographystyle{abbrvnat}
%\bibliographystyle{achemnat}
%\bibliographystyle{plainnat}
%\bibliographystyle{abbrv}
%\bibliographystyle{plain}
%\bibliographystyle{bioinformatics}
\bibliography{main}
